Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-25 paper/snakemajoranas.tex
Made system figure smaller
typo fixed

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/zigzag.pdf}
\caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
The yellow areas are the superconductors at a phase difference $\pm \phi / 2$.
The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
The modulation of the zigzag is parameterized by its amplitude $z_y$ and period $z_x$.
Inside the semiconductor we indicate the longest possible trajectory by the red curve.
\label{fig:setup}}
\end{figure}

@@

\comment{Disorder has a similar effect but one has no control over it.}
Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
However, in contrast to introducing weak disorder into a system, changing the geomerty is experimentally much easier to realize and therefore easier to control.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.75\columnwidth]{figures/zigzag.pdf}
\caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
The yellow areas are the superconductors at a phase difference $\pm \phi / 2$.
The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
The modulation of the zigzag is parameterized by its amplitude $z_y$ and period $z_x$.
Inside the semiconductor we indicate the longest possible trajectory by the red curve.
\label{fig:setup}}
\end{figure}

@@

\comment{Disorder has a similar effect but one has no control over it.}
Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
However, in contrast to introducing weak disorder into a system, changing the geometry is experimentally much easier to realize and therefore easier to control.
